\plaintitle

### 2017-04-29 statistical-quorum.tex
TODOs

@@

\subsection{Bayesian Theory}
After collecting an initial set of votes from members, we want to use that data to construct a prior distribution to help estimate the posterior probability that the proposal is acceptable to the entire community.  Because the sum of  the collected votes follows a binomial distribution, a commonplace and convenient choice for the form of the prior on the community's bias is the Beta distribution (due to its conjugacy with the binomial distribution).  Together, they form the Beta-binomial distribution (related to the P\'olya urn model).

@@

\todo[inline]{Theoretical evaluation, diagrams. Get readers to understand some of its properties visually:\\
4 Figures and 1 Table Pending}

@@

@@

\todo[inline]{Describe why is $0.90\%$ a reasonable statistical quorum and how to determine one for your community.}

@@

\todo[inline]{Security. How to prevent a group of people to vote and by trick reaching statistical quorum.
We use dynamic statistical quorum to address this, but one other approach is also for voting to stay open and
decisions can then be in the future revoked by people adding more votes, or changing them. But for some decisions
this might not really be possible, because decisions might not be reversible. You can revoke a law, but if you built
a building as a consequence of a decision?}

>>>>

\todo[inline]{Something we need to think about is the level of detail we want to go into regarding the implementation/features of PeerMind beyond statistical quorum and range voting.  I think we might want to focus on only those two features for this paper.\\
I think PeerMind as a comprehensive platform should have its own paper where all of the data is analyzed across the board.  This would be a much more typical HCI paper.  (If I can become president of Ridge in a future semester, we'll have another chance to run a clean, well-designed experiment with a much more developed version of PeerMind.)\\
The message in the current paper might be clearest if we keep the scope focused on the theory + evaluation/verification.  We should make sure we're not trying to pack too much into one paper.
\\---Max}

@@

\subsection{Bayesian Theory}

\todo[inline]{Weave in a single concrete example to ground all the abstract theory so that the entire derivation and motivation has a clear and cohesive thread from start to finish.}

After collecting an initial set of votes from members, we want to use that data to construct a prior distribution to help estimate the posterior probability that the proposal is acceptable to the entire community.  Because the sum of  the collected votes follows a binomial distribution, a commonplace and convenient choice for the form of the prior on the community's bias is the Beta distribution (due to its conjugacy with the binomial distribution).  Together, they form the Beta-binomial distribution (related to the P\'olya urn model).

@@

\todo[inline]{Visualize the credibility and dynamics of the voting process under this framework:\\
4 Figures and 1 Table Pending}

@@

\todo[inline]{See my comment at the beginning of the PeerMind Web App section.  I think the evaluation you note below about the interviews is out of the scope of this paper, which should be focused on statistical quorum and less online vs. offline platforms.\\
---Max}

@@

\todo[inline]{Describe why is $0.90\%$ a reasonable statistical quorum and how to determine one for your community.\\
Part of the answer here is honestly just that the admin should tune the threshold (and a few of the other hyperparameters we introduce) to their intuition.  Once you set the parameters, the real benefit is that you have consistency, rather than having to always use your intuition as an admin about evaluating credibility.}

@@

\todo[inline]{Security. How to prevent a group of people to vote and by trick reaching statistical quorum.
We use dynamic statistical quorum to address this, but one other approach is also for voting to stay open and
decisions can then be in the future revoked by people adding more votes, or changing them. But for some decisions
this might not really be possible, because decisions might not be reversible. You can revoke a law, but if you built
a building as a consequence of a decision?\\
(See near/post-quorum validation phase idea in GitHub issues as one suggested solution.)}
